\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-05-14 paper/ms.tex
Python bindings

There are several ways of using \pkg{DNest4}. After installing the software
(Section~\ref{sec:installation}), you can implement a model in \proglang{C++}
(Section~\ref{sec:models}) and compile it to create an executable file
to run \pkg{DNest4} on that problem. This method offers the flexibility

@@

\subsection{Python Bindings}

>>>>

There are several ways of using \pkg{DNest4}. After installing the software
(Section~\ref{sec:installation}), you can implement a model as
a \proglang{C++} class
(Section~\ref{sec:models}) and compile it to create an executable file
to run \pkg{DNest4} on that problem. This method offers full control over the
design of your class, and allows the opportunity (for example) to optimise
performance by preventing a full re-computation of the log-likelihood when
only a small subset of the parameters were changed.

Similarly, the \proglang{Python}
bindings (Section~\ref{sec:python_bindings}) allow you
to specify a model class in \proglang{Python}, and run \pkg{DNest4} entirely
in the \proglang{Python} interpreter without having to invoke the \proglang{C++}
compiler.

@@

\subsection{Python Bindings}\label{sec:python_bindings}
